\LaTeXe\ guide for the Journal of Functional Programming

### 2019-04-28 papers/jfp/8-engineering.tex
Add notes on some of the TODO's

\todo{AM}{Show implementation of \hs{computeND}}.

@@

\todo{AM/NM}{Re-using existing infrastructure: (a) key-value store, (b) remote execution service.}

@@

\todo{AM/NM}{We are talking about sets above, but are using lists, which is a
bit inconsistent. We could switch from \hs{[k]} to \hs{Set k} fairly easily.
Shall we?}

>>>>

\todo{AM}{Show implementation of \hs{computeND}. Neil says: not convinced it's that interesting.}.

@@

\todo{AM/NM}{Re-using existing infrastructure: (a) key-value store, (b) remote execution service. Neil says: I think this is a stretch. It's a lot more nuanced as we saw from Bazel discussions so I'd probably skip it.}

@@

\todo{AM/NM}{We are talking about sets above, but are using lists, which is a
bit inconsistent. We could switch from \hs{[k]} to \hs{Set k} fairly easily.
Shall we? Neil says: Haskell code dealing with sets is quite a lot more complex. People are used
to being quite fuzzy around the difference - I'd leave it as is.}
